\documentclass[margin,line]{res}
\usepackage{kotex}
\usepackage{xcolor}
\usepackage{hyperref}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\begin{document}
\name{황준오 Juno Hwang \vspace*{.1in}}
\begin{resume}
\section{Affiliation}
Department of Science Education (Physics Major), College of Education, Seoul National University

Data Science Lab, Ph.D Candidate

\section{\sc Contact}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
Room 412, Building 13, Seoul National University, 1 Gwanak-ro Gwanak-gu,    & {Phone:}  010 - 5650 - 7307 \\                   
Seoul 08826, Korea & {E-mail:}  wnsdh10@snu.ac.kr\\         
\end{tabular}

\section{\sc Education}

{\bf Seoul National University}, Seoul, Korea\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D Candidate, Data Science Lab, Science Education (Physics Major), 2021 $\sim$
\item[] Technical Research Personnel (Alternative Military Service), 2024 $\sim$
\end{list1}
{\bf Seoul National University}, Seoul, Korea\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Physics Education,  February 2021
\item[] B.S., Computational Science,  February 2021
\end{list1}


\section{\sc Teaching Experience}
\begin{list1}
    \item[] Seoul National University, Department of Physics Education, Teaching Assistant for 'Computational Physics and Education' (Spring 2024)
    \item[] Seoul National University, Center for Liberal Education, Head Teaching Assistant for 'Introduction to Computing' (2019 - 2023)
\end{list1}


\section{\sc License \& Certificate}
Teacher's Certificate, Secondary School Regular Teacher(Grade II) of Physics, Faburary 2021\\


\section{\sc Work  \phantom{MM} Experience}
{\bf LBox Co.}\\
\vspace*{-.1in}
\begin{list1}
\item[] Research Intern, 2021 Dec. $\sim$ 2022 Feb.
\item[] Document image enhancement and classification
\item[] OCR correction algorithm for legal documents
\end{list1}


\section{\sc Publications}
{\bf J. Hwang}, S. Hong, T. Eom \& C. Lim (2024). Enhancing Pre-service Teachers’ Competence with A Generative Artificial Intelligence-Enhanced Virtual Reality Simulation, ISLS 2024 Proceedings.

H. Soh, D. Kim, {\bf J. Hwang}, \& J. Jo (2023). Mirror descent of Hopfield model. Neural Computation, 35(9), 1529-1542.

{\bf J. Hwang}, W.S. Hwang, \& J. Jo (2020). Tractable loss function and color image generation of multinary restricted Boltzmann machine. NeurIPS 2020 DiffCVGP Workshop.


%\section{\sc Manuscripts under review \& \\ in preparation}


\section{\sc Invited \phantom{MM} Seminars}
2024 KIAS CAC Summer School on the Parallel Computing and Artificial Intelligence\hfill Seoul\\
2023 KIAS CAC Summer School on the Parallel Computing and Artificial Intelligence\hfill Seoul\\
2023 KIAS Center for AI and Natural Sciences Winter Workshop\hfill Gangwon\\
2022 KIAS Winter School for Physics and Machine Learning \hfill Online\\
2021 APCTP Workshop for Physics and Machine Learning \hfill Jeju\\


\section{\sc Poster \& Oral Presentations}
2024 International Conference on Science Education in the Infosphere \hfill Seoul\\
2024 International Society of Learning Sciences Annual Meeting\hfill Buffalo\\
2024 한국문화재보존과학회 춘계학술대회 \hfill Seoul\\
2023 한국교육공학회-한국교육정보미디어학회 추계공동학술대회 \hfill Seoul\\
2022 한국현장과학교육학회 정기학술대회\hfill Seoul\\
2020 Neural Information Processing Systems (DiffCVGP workshop)  \hfill Online\\
2018 American Association of Physics Teachers Winter Meeting \hfill California\\

\section{\sc Awards}

최우수논문상, 2023 한국교육공학회-한국교육정보미디어학회 추계공동학술대회 \\
Award in 2018 Big Data \& A.I. Contest, Korea East-West Power Co., Ltd.\\
Excellence Award in 2016 Wearable Computer Contest, KAIST\\
First Prize in 2013 Big Data Fair, Ministry of Science, ICT and Future Planning\\
Silver Prize in 2012 Korea Wi.Content Contest



\end{resume}
\end{document}